---
title: "colPalette_vignett"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{colPalette_vignett}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

**colPalette** is designed to help users create unique color palettes that are specific to the image analysis they are are conducting. Upon taking input as a series of hexadecimal color codes, this package will create a plain english version of each color, a color palette as stacked bars, and a color palette as a color wheel.

Within this package, there are three functions that take a dataframe of hexadecimal color codes as input. 
  crePalette(col) is designed to convert the hexadecimal color codes into a plain english version of each color. 
  plotPalette(col, num) is designed to convert the hexadecimal color codes into a stacked color palette for easy visualization of the utilized colors.
  plotCircPalette(col, num) is designed to convert the hexadecimal color codes into a color wheel for easy visualization of the relationships between each color. 



```{r setup}
library(colPalette)

#example color set
colors <- data.frame(HEX = c('#FF0000FF', '#80FF00FF', '#00FFFFFF', '#8000FFFF', '#E7298A'))
num <- 5

#convert hexadecimal color codes to plain language
newPalette <- crePalette(colors)
newPalette 

#convert hexadecimal color codes into stacked color palette
newStackedPalette <- plotPalette(colors, num)

#convert hexadecimal color codes into color wheel palette
newWheelPalette <- plotCircPalette(colors, num)

```
